### 2012-06-14 inst/examples/value_of_information.Rmd
value-of-information for corner case scenarios
value-of-information for corner case scenarios, now with plots

value <- melt(data.frame(stock = x_grid, det=det$V g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
````

@@

```{r }
base <- simulatereps(det, 0, 0, 0)
full <- simulatereps(gmi, .2, .2, .2)
cautious <- simulatereps(gmi, 0, 0, 0)
reckless <- simulatereps(det, .2, .2, .2)
````

@@

``` {r biblio, echo=FALSE, results="asis"}
I(knitcitations::bibliography())
````

>>>>

value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
````

@@

```{r }
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .2, .2, .2)
````

```{r }
full <- simulatereps(gmi, .2, .2, .2)
cautious <- simulatereps(gmi, 0, 0, 0)
````

@@

``` {r biblio, echo=FALSE, results="asis"}
I(print(knitcitations::bibliography(), "html"))
````
